
%\hfil{\Large{\bf Further Education}}\hfil\\
%\nameskip\break
\begin{rSection}{Online certificates}
  \begin{itemize}
    %
    \item{\it Taming Big Data with Apache Spark and Python - Hands On!} -- by Sundog Education on Udemy. \href{https://www.udemy.com/certificate/UC-G53DWS5V/}{Certificate} earned on April 15, 2019.
    %
    \item {\it Practical Reinforcement Learning} -- National Research University Higher School of Economics on Coursera. \href{https://coursera.org/share/7dbaef1de4f13d7016316a4dd7eece8a}{Certificate} earned on February 14, 2019.
    %
    \item{\it Deep Learning, a 5-course specialization} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/47b1d9ff10e34c9d26c75f5f0914379b}{Certificate} earned on January 7, 2019.
    %
    \subitem {\it Neural Networks and Deep Learning} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/b99cfdbf684af876690916f62a41f74d}{Certificate} earned on December 11, 2018.
    %
    \subitem {\it Improving Deep Neural Networks: Hyperparameter tuning, Regularization and Optimization} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/70436cea6ad8695c56da96f285739488}{Certificate} earned on December 21, 2018.
    %
    \subitem {\it Structuring Machine Learning Projects} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/b4fec0b5c8ada28277e0369aced10c34}{Certificate} earned on December 24, 2018.
    %
    \subitem {\it Convolutional Neural Networks} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/efaf45dddda63778f97da9aafaaa71b0}{Certificate} earned on December 30, 2018.
    %
    \subitem {\it Sequence Models} -- deeplearning.ai on Coursera. \href{https://coursera.org/share/aeb503aafcd63fd9b1e098c232c6cfa4}{Certificate} earned on January 7, 2019.
    %
    \item {\it Google Cloud Platform Big Data and Machine Learning Fundamentals} -- by Google Cloud on Coursera. \href{https://coursera.org/share/469ce1832e0392458bc6930beb44d8c6}{Certificate} earned on October 1, 2018.
  \end{itemize}
\end{rSection}

% Talks 
\begin{rSection}{Talks}
  \begin{itemize}
  	\begin{rSubsection}{Public talks}{}{}{}
       	\item{\it Next Gen Railway Asset Management} (with Jasper Derikx) - PyData Eindhoven - Eindhoven, the Netherlands (29-30 November 2019)
	\item{\it Next Gen Railway Asset Management} (with Oscar van Hees) - Big Data Expo - Jaarbeurs, Utrecht, the Netherlands (18-19 September 2019)
	\end{rSubsection}
	 %
  	\begin{rSubsection}{Podcasts}{}{}{}
       	\item De Dataloog: 
   	\href{https://www.dedataloog.nl/uitzending/dtl-big-data-expo-special-8-het-belang-van-onzekerheid-bij-ml-modellen/}{Het belang van onzekerheid bij ML modellen}.
	\end{rSubsection}
	%
  \end{itemize}
\end{rSection}

% Talks 
\begin{rSection}{Workshops}
  \begin{itemize}
       	\item Bayesian methods in machine learning - Vantage AI (November - December 2019)
	\item Computer vision with Tensorflow 2.0 - Vantage AI (July - August 2019)
  \end{itemize}
\end{rSection}