%\begin{itemize}
\item Ruben Dekker, 2025, UU, Utrecht - M.Sc. Neuroscience and Cognition "Combining Macronutrients, Micronutrients, and Processing to Measure Nutritional Value" (with M. Menassa)
\item Andrei Dobrea, 2025, UU, Utrecht - M.Sc. Artificial Intelligence "Predicting the outcome of birth asphyxia in infants" (with A. Feelders and T. Alderliesten)
\item Niels Helmantel, 2024, UU, Utrecht - M.Sc. HCI "Design of an Explainable Interface for a Sepsis Prediction Algorithm" (with H. Hauptmann \& D. Vijlbrief)
\item Max Botman, 2024, UU, Utrecht - M.~Sc.~ADS "Developing innovative methods for measuring body temperature
in preterm infants to enhance prediction of late-onset sepsis" (with D.~Vijlbrief and A.~de Hond)
\item Paula Romero Jim\'{e}nez, 2024, UU, Utrecht - M.~Sc.~ADS "Using temperature data to predict late-onset
sepsis in preterm infants" (with D.~Vijlbrief and A.~de Hond)
\item Selin Acan, 2023, UvA, Amsterdam - M.Sc. software engineering "Prediction of the Outcome of Asphyxia Patients After Hypothermic Treatment with Continuous Variables" (with T. Alderliesten)
\item Annie Clarnette, 2022, UU, Utrecht - M.Sc. ADS "Explainable machine learning algorithm for early prediction of late-onset sepsis in preterm infants using real-time catheter data" (with D. Vijlbrief)
\item Felix Bindt, 2022, UU, Utrecht - M.Sc. ADS "Predicting Late-Onset Sepsis using Machine Learning with a Minimum Feature, Blood Pressure Centered, Clinic Oriented Approach" (with D. Vijlbrief)
\item Joshua Oosterlaken, 2022, UU, Utrecht - M.Sc. ADS "The prediction of late-onset sepsis using generalized additive models" (with D. Vijlbrief)
\item Kathleen Short, 2017, UvA, Amsterdam - M.Sc. Physics "Millisecond Pulsars and the Galactic Centre GeV Excess: Prospects for e-ASTROGAM" (with C. Weniger) 
%\end{itemize} 
